Describe and Explore: Using feature-based time series clustering to identify meaningful structures in intensive longitudinal data

### 2023-01-17 manuscript.tex
:memo: illustration intro

\section{Empirical Illustration}
To illustrate common use cases of feature-based time series clustering with psychological ESM data, we apply the clustering process to a recent set of studies that collected diverse concepts with context-specific measurements. The illustration specifically uses data from research on migration experiences, where researchers have started using ESM data to follow the daily interactions of migrants with the cultural majority groups \citep[e.g.,][]{Keil2020}. This new type of research comes as a response to prominent reviews, which have called for more longitudinal \citep[e.g.,][]{Ward2019} and real-world data \citep[e.g.,][]{McKeown2017}. At the same time, conceptual works have pushed for more diverse assessments of migration experiences, including motivational, affective, cognitive, and behavioral aspects \citep[e.g.,][]{Kreienkamp2022d}. The migration ESM research, thus, offers a good example of the modern ESM data that introduces diverse conceptualizations and more event-specific missingness patterns.

>>>>

\section{Empirical Illustration}
To illustrate common use cases of feature-based time series clustering with psychological ESM data, we apply the clustering process to a recent set of studies that collected diverse concepts with context-specific measurements. The illustration specifically uses data from research on migration experiences, where researchers have started using ESM data to follow the daily interactions of migrants with the cultural majority groups \citep[e.g.,][]{Keil2020}. This new type of research comes as a response to prominent reviews, which have called for more longitudinal \citep[e.g.,][]{Ward2019} and real-world data \citep[e.g.,][]{McKeown2017}. At the same time, conceptual works have pushed for more diverse assessments of migration experiences, including motivational, affective, cognitive, and behavioral aspects \citep[e.g.,][]{Kreienkamp2022d}. The migration ESM research, thus, offers a good example of the ESM data that introduces diverse conceptualizations and more event-specific missingness patterns.
